Corporate Security Solutions for BYOD.\\ A Novel User-Centric and Self-Adaptive System

### 2015-04-15 MUSES_vs_BYOD_solutions.tex
Last revision to section 3, so this closes #4

Features in Blackberry Balance are similar. This security package was announced as a feature of BlackBerry 10. Nevertheless, it is available with BlackBerry Enterprise Service 10, which is a device management, security and app management for BlackBerry, iOS and Android devices. It is necessary to activate BlackBerry Balance for having available some security features, all related or similar to the aforementioned. For instance, a message is displayed when the user tries to copy work data and then paste it into personal apps. Also, user attempting for actions that are not permitted in the company ISP, or may cause secure work information to be in contact with personal applications, these actions won't be permitted.

>>>>

Features in Blackberry Balance are similar. This security package was announced as a feature of BlackBerry 10. Nevertheless, it is available with BlackBerry Enterprise Service 10, which is a device management, security and app management for BlackBerry, iOS and Android devices. It is necessary to activate BlackBerry Balance for having available some security features, all related or similar to the aforementioned. For instance, a message is displayed when the user tries to copy work data and then paste it into personal apps. Also, user attempting for actions that are not permitted in the company ISP, or may cause secure work information to be in contact with personal applications, these actions will not be permitted.
